%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Peter To} % Name
\address{1927 Red Sage, Irvine, CA 92618 \textbar\ +1 (408) 507-1728 \textbar\ peterto1998@gmail.com} % Address, phone number and email
\address{LinkedIn: www.linkedin.com/in/petertochunhim} %LinkedIn url


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill {\bf {Berkeley, CA}} %school & location
\\ {\it B.A. Economics} \hfill {\em August 2018 - May 2020} %major & year
\begin{itemize}
    \item {\bf Overall GPA:} 3.94/4.0 
    \item {\bf Relevant Coursework:} Intermediate Micro- and Macro-Economics, Financial Economics, International Trade, Data Science, Probability and Statistics
    \item {\bf Honors:} Dean’s Honor List, UC Berkeley Transfer Scholarship
\end{itemize}

{\bf University of California, Irvine} \hfill {\bf {Irvine, CA}} %school & location
\\{\it B.A. Business Administration, Emphasis in Accounting (not completed)} \hfill {\em Sep 2016 - June 2018} %major & year
\begin{itemize}
    \item Finished all accounting emphasis courses
    \item {\bf Relevant Coursework:} Financial and Managerial Accounting, Auditing, Corporate Finance, Individual Taxation, Accounting Information System
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{UC Berkeley Osher Lifelong Learning Institute}{\bf {Berkeley, CA}}{Student Assistant}{Sep 2018 - Present}
\begin{itemize}
    \item Assist lecturers in classroom instruction and provide support and guidance to students and guests.
    \item Ensure smooth class flow and assist in classroom coordination.
    \item Provide technical support for supervisors.
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Union Medical Healthcare Limited}{\bf {Kowloon, Hong Kong}}{Administrative Clerk}{Aug 2017 - Sep 2017}
\begin{itemize}
    \item Compiled, sorted, and processed more than 1000 customer information and treatment records by Excel.
    \item Helped prepare guidelines for doctors and staff and consent forms for customers.
    \item Organized and updated company files, sorted incoming mails and other documents.
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Moore Stephens CPA Limited Hong Kong}{\bf {Kowloon, Hong Kong}}{Audit Intern}{Jun 2017 - Aug 2017}
\begin{itemize}
    \item Examined financial documents for clients and ensured that the financial records are accurate.
    \item Prepared audit working papers using Microsoft Excel and Word and auditing software.
    \item Contacted with clients and independent parties to request financial information through phone and email.
\end{itemize}
\end{rSubsection}

\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 

\begin{rSubsection}{UC Berkeley HKSA Intramural Volleyball Team}{\bf {Berkeley, CA}}{Team Captain}{Sep 2018 - Present}
\begin{itemize}
    \item Led the team to intramural Co-Rec volleyball playoffs in Fall 2018.
    \item Recruit players and organize team practices and other events.
    \item Effectively communicate with team members, other teams’ captains, officials, and supervisors.
\end{itemize}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% Other Skills
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Skills}

{\bf Languages:} Fluent English, Native Cantonese, Fluent Mandarin %language
\item {\bf Skills:} Microsoft Office (Excel, Word, PowerPoint), Programming R, Mac OS and Windows, Social Media (Facebook, Instagram, Snapchat), Typing 50wpm, Video Editing %skills
\item {\bf Interests:} Sports (Volleyball, Basketball, Soccer), Traveling, Video games %interests

\end{rSection}

\end{document}
